Updated results

### 2018-07-15 paper/Chapters/Chapter2.tex
MLCA updated results shared with super

%-----------------------------------
%	SECTION 1
%-----------------------------------
\section{Latent class analysis (LCA)}\vspace{-0.3cm}

>>>>

%-----------------------------------
%	SECTION 1
%-----------------------------------
\section{Dietary diary collected in the NDNS RP}\vspace{-0.3cm}

Participants were asked to keep a record of everything eaten or drunk over four consecutive days. Interviewers undertook three visits with each participant. At the first visit, the interviewer explained the method followed a protocol, taking participants through the sections in the diary including how to describe details of food and drink and portion size and an example day. The second was a brief visit to check for compliance, answer questions or deal with problems and review the diary to identify and edit possible omissions and missing detail. The third visit was to collect the diary and again review and edit possible omissions.

In the diary, participants were asked to record portion sizes in household measures (e.g. one tablespoon of beans, one Kit Kat finger-size), or for packaged foods to note the weight indicated on the packet. For homemade dishes, participants were asked to record on a separate page in the diary the individual ingredients and quantities for the whole dish along with a brief description of the cooking method and how much of dish they had consumed. In addition to details of what and how much was eaten, participants recorded for each eating occasion; when was it, where they were, who they were eating with. An example, used as guidance for participants, of a food diary for one day is shown in \textbf{Appendix \ref{AppendixC}}.

%-----------------------------------
%	SECTION 2
%-----------------------------------
\section{Latent class analysis (LCA)}\vspace{-0.3cm}

### 2018-07-15 results/results.Rmd
MLCA updated results shared with super

# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 25%, 50%, 75%)

@@

# Mixed effect LCA with carbohydrates intake groups redefined: (cutoff = 50%)

>>>>

# ~~Mixed effect~~ LCA with carbohydrates intake groups redefined: (cutoff = 25%, 50%, 75%)

@@

# ~~Mixed effect~~ LCA with carbohydrates intake groups redefined: (cutoff = 50%)
